Bird beak's elaboration and exploration

### 2021-11-22 Analysis/02.1-shapespace_allbirds_lvl_superorder_order.Rmd
Update 02.1-shapespace_allbirds_lvl_superorder_order.Rmd

```{r}
## Preparing the model files
model_list <- list()
class(model_list) <- c("beer", "mini.chains")
models_path <- "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/cluster/"
## Getting all the model files
model_files <- list.files(models_path, pattern = ".rda")
## Get the first model
load(paste0(models_path, model_files[1], collapse = "/"))
print(model_files[1])
## Clean the bits that are not going to be used (but are huge)
model[[1]][c("error.term", "family", "y.additional", "ginverse", "ZR")] <- NULL
## Update the model list
model_list[[length(model_list)+1]] <- model[[1]]
model <- NULL
model_files <- model_files[-1]

@@

## Checking the diagnosis

## Saving the results
save(shapespace_allbirds_lvl_superorder_order, file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.MCMCglmm")

>>>>

```{r, eval = FALSE}
## Preparing the model files
model_list <- list()
class(model_list) <- c("beer", "mini.chains")
models_path <- "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/cluster/"
## Getting all the model files
model_files <- list.files(models_path, pattern = ".rda")
## Get the first model
load(paste0(models_path, model_files[1], collapse = "/"))
print(model_files[1])
## Clean the bits that are not going to be used (but are huge)
model[[1]][c("error.term", "family", "y.additional", "ginverse", "ZR")] <- NULL
## Update the model list
model_list[[length(model_list)+1]] <- model[[1]]
model <- NULL
model_files <- model_files[-1]

@@

## Saving the results
save(shapespace_allbirds_lvl_superorder_order, file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.MCMCglmm")
```

## Checking the mini chains' ESSs

```{r, eval = TRUE}
